Selective electroporation of the viral envelope

### 2021-04-08 documents/pure_electroporation.tex
Fiiine I'll do it numerically

There, the relevant time constants referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to ion diffusion and capacitive charging. The relevant damage quantities were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.

@@

Viruses have extraordinary mechanical properties\footnote{Why is this? What selection pressures drive the selected pressure?}, so it seems reasonable that their dielectric properties could differ substantially from that of other structures. In the case of bacteriophages, the genome is packaged so tightly that the core is best considered an amorphous, glass-like material. ssRNA viruses like coronaviridae are perhaps somewhat less . On the other hand, the human "structome" also contains countless lipid vesicles that might plausibly

The most obvious difference is scale. Viruses are minute. The classic Schwan equation implies that the transmembrane voltage

@@

@@

>>>>

While both mechanisms time constants, those discussed in the previous paper referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging and ion diffusion. The relevant damage quantities were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.

@@

Viruses have extraordinary mechanical properties\footnote{Why is this? What selection pressures drive the selection of this pressure?}, so it seems reasonable that their dielectric properties could differ substantially from that of other structures.

In the extreme case of the bacteriophage, the genome is packaged so tightly into the protein capsid that the core is often described as a glassy crystal of DNA\cite{Conformation2007}. ssRNA viruses like coronaviridae are perhaps somewhat less.

On the other hand, the human "structome" also contains countless lipid vesicles that might plausibly

@@

The most obvious difference is scale. Viruses are minute. The classic Schwan equation implies that the transmembrane voltage is proportional to

There are two characteristic time constants; a low and a high-frequency one.

@@

\subsection{Optimal pulse}

This bears considerable similarity to e.g. radar waveform design and compressed sensing.

Lagrange multipliers. Unfortunately, while closed-form solutions appear to be readily available for some simplified cases (such as when the membrane is infinitesimally thin),

The impulse response is the derivative of the step response. The convolution integral (or sum, in the discrete case) can be performed
